### 2018-08-14 methods.tex
fixing stuff

\subsubsection{Fuel material flows}
The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
Protactinium presents a challenge, since it has a large absorption cross 
section in the thermal energy spectrum. Accordingly, $^{233}$Pa is continuously 
removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
system is designed to separate $^{233}$Pa from the molten-salt fuel over 3 
days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
primary loop. This feature allows the reactor to avoid neutron losses to 
protactinium, keeps fission products to a very low level, and increases the 
efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
full list of nuclides and the cycle times used for modeling salt treatment and 
separations \cite{robertson_conceptual_1971}.

>>>>

\subsubsection{Fuel material flows}
The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
Protactinium presents a challenge, since it has a large absorption cross 
section in the thermal energy spectrum. Accordingly, $^{233}$Pa is continuously 
removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
to decay to $^{233}$U without poisoning the reactor. The reactor reprocessing 
system must separate $^{233}$Pa from the molten-salt fuel over 3 
days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
primary loop. This feature allows the reactor to avoid neutron losses to 
protactinium, lowers in-core fission product inventory, and increases the 
efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
full list of nuclides and the cycle times used for modeling salt treatment and 
separations \cite{robertson_conceptual_1971}.
